### 2023-06-28 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny at intro2
yny at intro3

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, as the basic structural units for compartmentalizing biological systems, 
have been observed to contain a vast array of proteins and different lipid species, that phase-separate and form domains or rafts, resulting in spatial variations in material properties such as bending stiffness \cite{}. Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes composed of different lipid species, have been used to study the rich patterns and accompanying morphologies which emerge from elastic heterogeneity in the membrane.  In a quiescent environment, inhomogeneity in a vesicle membrane bending stiffness may give rise to change in vesicle morphology \cite{Lowengrub2009_PRE}, closely related to cellular budding and fission processes \cite{Rauch2000_BriophysJ} as well as in membrane adhesion and fusion \cite{Takeda2003_PNAS}.

Under a linear shear flow, a multicomponent vesicle exhibits exotic dynamics in both shape and membrane composition \cite{Liu2017_SoftMatter,Gera2018_SoftMatter,Gera2022_JFM}. The vesicle hydrodynamics is characterized by parameters such as the capillary number, reduced volume, and
confinement ratio. Understanding these dynamics is critical to
understanding biophysical and microfluidic processes. For example, a
vesicle's reduced area and viscosity contrast will determine if it
undergoes tank treading, swinging, or tumbling in a shear
flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
these shapes include axisymmetric bullets or parachutes, and asymmetric
parachutes. More recently, groups have considered these transitions when
vesicles are suspended in a channel or pipe
flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and
swirling behaviors; croissant and slipper shapes; and semipermeability.

>>>>

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, as the basic structural units for compartmentalizing biological systems, 
have been observed to contain a vast array of proteins and different lipid species, that phase-separate and form domains or rafts, resulting in spatial variations in material properties such as bending stiffness \cite{}. Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes composed of different lipid species, have been used to study the rich patterns and accompanying morphologies which emerge from elastic heterogeneity in the membrane.  In a quiescent environment,  such elastic heterogeneity gives rise to wrinkling budding \cite{Lowengrub2009_PRE,Li2012_CommMathSci}, adhesion and fusion \cite{Zhao2011_PRE} of vesicle membrane, closely related to cellular budding and fission processes \cite{Rauch2000_BriophysJ} as well as in cellular adhesion and fusion \cite{Takeda2003_PNAS}.

Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Gera2018_SoftMatter,Gera2022_JFM} than a single component vesicle \cite{Abreu2014_ACI}.
%
%Sohn et al. (2010) studied two-dimensional multicomponent vesicles in a background shear flow, along with the evolution of distinct surface phases, finding highly complex morphologies and dynamics for highly deformed vesicles. Smith & Uspal (2007) showed using dissipative particle dynamics simulations that a shear flow can be used to separate buds from a multicomponent vesicle. The influence of both bending rigidity and spontaneous curvature variation on the equilibrium shape of a vesicle has also been investigated (Cox & Lowengrub 2015). Subsequent boundary integral simulations by Liu et al. (2017) showed a transition from tumbling to tank-treading to ‘phase-treading’ of the constituents along the surface upon increasing the shear rate. Analytic results have also shown that a variation of bending rigidity along a surface can induce migration in tank-treading vesicles (Olla 2011). Synthetic systems have also been fruitful for testing theoretical predictions. Experiments using a two-phase lipid vesicle in such a flow as a simplified model of red blood cell dynamics showed similarly complex features (Tusch et al. 2018). Gera & Salac (2018b) then used simulations to probe a wide array of morphological changes due to spatially varying bending stiffness and line tension between two lipid phases. The phase separation process itself is naturally of great interest, and experiments have been used to study spinodal decomposition and viscous fingering along membrane surfaces (Veatch & Keller 2003; Lowengrub, Rätz & Voigt 2009; Marenduzzo & Orlandini 2013; Stanich et al. 2013).
%
The vesicle hydrodynamics is characterized by parameters such as the capillary number, reduced volume, and
confinement ratio. Understanding these dynamics is critical to
understanding the biophysics of red blood cells (RBCs) in blood flow. For example, a
vesicle's reduced area and viscosity contrast will determine if it
undergoes tank treading, swinging, or tumbling in a shear
flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
these shapes include axisymmetric bullets or parachutes, and asymmetric
parachutes. More recently, groups have considered these transitions when
vesicles are suspended in a channel or pipe
flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and
swirling behaviors; croissant and slipper shapes; and semipermeability.
